CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-10 paper.Rmd
Fixing the script
Minor changes.

The steps to create the PSUT matrices for each country and each year
are accomplished by a
[targets][link-targets] [@Landau:2021aa]
computation pipeline
available in the [PFUDatabase][link-pfudatabase]
package.
A unique feature of the
[PFUDatabase][link-pfudatabase]
pipeline is an innovative exemplar system that allows
analyses to proceed when allocation or efficiency data for a country are unavailable.
When allocations or efficiencies are missing,
a string of exemplar countries are queried for the required information.
For example, exemplars for Belgium are
France, Europe, and ultimately, the World, in that order.
The design of the calculation pipeline in the [PFUDatabase][link-pfudatabase] package 
allows allocation and efficiency data
for any country or year to be added at a later date 
to improve the database.

@@

```{r}
library(targets)
# Run the PFUDatabase pipeline
# targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))

>>>>

The steps to create the PSUT matrices for each country and each year
are accomplished by a
[targets][link-targets] [@Landau:2021aa]
computation pipeline
available in the [PFUDatabase][link-pfudatabase]
package.
A unique feature of the
[PFUDatabase][link-pfudatabase]
pipeline is an innovative exemplar system that allows
analyses to proceed when allocation or efficiency data are unavailable for a country.
When allocations or efficiencies are missing,
a string of exemplar countries or regions
are queried for the required information.
For example, exemplars for Belgium are
France, Europe, and ultimately, the World, in that order.
The design of the calculation pipeline in the [PFUDatabase][link-pfudatabase] package 
allows allocation and efficiency data
for any country or year to be added at a later date 
to improve the database.

@@

```{r}
# Download FAO data for animal muscle work
source(file.path("ExampleFolder", "DownloadScripts", "download_amw_data.R"))
library(targets)
# Run the PFUDatabase pipeline
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))
